Market Expectations and Mangerial Turnover

### 2024-06-05 paper_new.qmd
updates to LLM work and paper_new.qmd · 92884aab - Gogs

---
title: "Market Expectations and Mangerial Turnover"
author: 
  - Ronan Gallagher
  - Barry Quinn
format: 
    pdf:
      fig-pos: "H"
bibliography: references.bib
execute: 
  echo: false
  warning: false
  message: false
---

@@

```{r}
spells |> 
  filter(staff_position=="manager" & national_team =="No" & youth_team=="No") |> 
  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
  group_by(season_start,national_team) |>
  count(season_start)  |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Manager-Club spells per annum", x = "Season Start Year", y = "Number of Turnovers") +
  theme_minimal() -> spell_count
plotly::ggplotly(spell_count)
```

```{r}
library(clipr)
unique(spells$Country) |> write_clip()
```

```{r}
# Assuming the LLM output is stored in a variable called 'llm_output'
categories <- unique(spells$Country)

# Remove leading/trailing whitespace and convert to lowercase
categories <- trimws(categories)
categories <- tolower(categories)

# Remove any leading/trailing punctuation marks
categories <- gsub("^[[:punct:]]+|[[:punct:]]+$", "", categories)

# Replace ' - ' and ' . ' with '.'
categories <- gsub(" - | \\. ", ".", categories)

# Replace 'not applicable', 'none', 'unknown', 'not found', 'not available', 'n/a' with NA
categories[categories %in% c("not applicable", "none", "unknown", "not found", "not available", "n/a","","0")] <- NA

# Categorize responses indicating LLM cannot find answer
llm_cannot_answer <- grepl("^i am not|^i cannot|^i don't|^i am just an ai|^i'm just an ai", categories)
categories[llm_cannot_answer] <- "LLM cannot find answer"

# Remove rows with NA values
categories <- categories[!is.na(categories)]

# Remove duplicate categories
categories <- unique(categories)

# Sort the categories alphabetically
categories <- sort(categories)
categories <- trimws(categories)
# Print the cleaned categories
unique(categories) |> write_clip()
```

```{r}
library(countries)
list_countries() |> length()
```

```{r}
# Assuming the list is stored in a variable called 'categories'
countries <- gsub("^.*\\b(\\w+)\\.*$", "\\1", spells$Country, perl = TRUE)

# Replace common non-country phrases with NA
non_countries <- c("based on my training data", "based on training data", "LLM cannot find answer", "none", "not applicable", "not found in my training data", "not sure", 
                   "unknown", "soccer", "tennis", "world cup", "football soccer", "northern", 
                   "rome", "soccer football", "west africa", "south america", "central america", 
                   "eastern europe", "north macedonia", "fifa", "uefa", "asia", "eu", "uefa european football association","uefa european", "eurozone", "caribbean", "cricket", "\\bi'm.*", "\\bi have.*", "\\bi cannot.*", 
                   "\\bi don't.*", "\\bi couldn't.*", "\\bna\\b", "\\bn/a\\b", "i can","\\bi am not aware","i am", "answer:", "africa", "europe", 
                   "middle east", "east germany", "soviet union", "uae", "uk", "usa", "world")
countries[countries %in% non_countries] <- NA

# Remove any leading/trailing whitespace
countries <- trimws(countries)

# Replace empty strings with NA
countries[countries == ""] <- NA

# Merge similar country names
# Create a named vector for country name mappings
country_mappings <- c(
  "_England_" = "England",
  "_Belgium_" = "Belgium",
  "_Germany_" = "Germany",
  "_Italy_" = "Italy",
  "_Serbia_" = "Serbia",
  "England -" = "England",
  "States" = "United States",
  "United States -" = "United States",
  "Kingdom" = "United Kingdom",
  "United Kingdom UK -" = "United Kingdom",
  "Democratic Republic of Congo" = "Democratic Republic of the Congo",
  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
  "Soviet Union" = "Russia",
  "Soviet Union former" = "Russia",
  "Soviet Union formerly" = "Russia",
  "Russia formerly Soviet Union" = "Russia",
  "Yugoslavia" = "Serbia",
  "Yugoslavia now Serbia" = "Serbia",
  "Yugoslavia or SFR Yugoslavia" = "Serbia",
  "Serbia formerly Yugoslavia" = "Serbia",
  "East Germany" = "Germany",
  "East Germany GDR" = "Germany",
  "East Germany Germany" = "Germany",
  "East Germany Germany Democratic Republic" = "Germany",
  "Macedonia" = "North Macedonia",
  "Macedonia formerly known as the Republic of Macedonia" = "North Macedonia",
  "Burma" = "Myanmar",
  "Myanmar Burma" = "Myanmar",
  "Congo" = "Democratic Republic of the Congo",
  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
  "Ivoire" = "Ivory Coast",
  "Holland" = "Netherlands",
  "Holland Netherlands" = "Netherlands",
  "United Arab Emirates UAE" = "United Arab Emirates",
  "UAE United Arab Emirates" = "United Arab Emirates",
  "United Kingdom UK" = "United Kingdom",
  "UK" = "United Kingdom",
  "ANDORA" = "Andorra",
  "Faso" = "Burkina Faso",
  "Rica" = "Costa Rica",
  "Salvador" = "El Salvador"
)

# Merge similar country names using the country_mappings vector
for (i in seq_along(countries)) {
  if (countries[i] %in% names(country_mappings)) {
    countries[i] <- country_mappings[countries[i]]
  }
}

# Handle historical country names
countries[countries == "Czechoslovakia"] <- NA  # Czechoslovakia no longer exists, split into Czech Republic and Slovakia

# Remove additional non-country values
non_countries <- c("International", "UEFA", "FIFA", "UEFA European", "European", "AFC", "GDR", "EU", "Eurozone", "UEFA European Football Union")
countries[countries %in% non_countries] <- NA

# Print the extracted country names
#countries |> table() |> sort(decreasing = TRUE)
unique(countries) |> write_clip()
```

```{r})
```

```{r}
table(countries) |> sort(decreasing = TRUE)
```

@@

```{r}
logit_baseline |>
  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
         "Cumulative Relative Strength"=b_Standardized_CumRS)

          |>
  pivot_longer(!.draw &!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
  ggplot(aes(y = fixed_effect,
             x=draws)) +
  stat_slab() +
  labs(x="",
       title="Baseline model for probability of poaching",
       subtitle="Posterior probability distribution",
       y="Fixed Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)

@@

```{r}
logit_baseline |>
  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
         "Cumulative Relative Strength"=b_Standardized_CumRS)
  pivot_longer(!.draw&!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
  ggplot(aes(y = fixed_effect,
             x=draws)) +
  stat_slab() +
  labs(x="",
       title="Baseline model for probability of poaching",
       subtitle="Posterior probability distribution",
       y="Fixed Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)

```{r}
logit |> 
  ungroup() |>
  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
  group_by(cty_factor,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(cty_factor,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effect on probability of poaching",
       subtitle="Posterior probability distribution",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)

>>>>

---
title: "Market Expectations and Mangerial Turnover"
author: 
  - Ronan Gallagher
  - Barry Quinn
format:
  pdf: default
  elsevier-pdf:
    keep-tex: true    
    fig-pos: "H"
bibliography: references.bib
execute: 
  echo: false
  warning: false
  message: false
---

@@

```{r}
spells |> 
  filter(staff_position=="manager" & national_team =="No" & youth_team=="No") |> 
  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
  group_by(season_start,national_team) |>
  count(season_start)  |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Manager-Club spells per annum", x = "Season Start Year", y = "Number of Turnovers") +
  theme_minimal() -> spell_count
spell_count
```

@@

```{r}
logit_baseline |>
  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
         "Cumulative Relative Strength"=b_Standardized_CumRS) |>
  pivot_longer(!.draw &!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
  ggplot(aes(y = fixed_effect,
             x=draws)) +
  stat_slab() +
  labs(x="",
       title="Baseline model for probability of poaching",
       subtitle="Posterior probability distribution",
       y="Fixed Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)

@@

```{r}
logit_baseline |>
  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
         "Cumulative Relative Strength"=b_Standardized_CumRS) |>
  pivot_longer(!.draw & !.iteration &!.chain,names_to = "fixed_effect",values_to = "draws")|>
  ggplot(aes(y = fixed_effect,
             x=draws)) +
  stat_slab() +
  labs(x="",
       title="Baseline model for probability of poaching",
       subtitle="Posterior probability distribution",
       y="Fixed Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
